---
title: "master.rmd"
author: Ben Marwick
date: Tuesday, April 01, 2014
output: html_document
---

Working with the images from LR9, ME2 & 3, LR12, mtbehn surface 2, japi

need to edit filenames to make this work!

```{r}
# get data, change this to your Dropbox location
image_files <- "C:\\Users\\marwick\\UW-Dropbox\\Dropbox\\Malonys-lithic-scan-data"
dirs <- dir(image_files, full.names = TRUE)

# get jpgs in each directory
jpgs <- list.files(dirs, pattern = "jpg|JPG$", recursive = TRUE, full.names = TRUE)

# how many jpgs per directory?
count_jpgs <- sapply(dirs, function(i) length(list.files(i, pattern = "jpg|JPG$", full.names = TRUE)))

# make easy to read data frame
count_jpgs_df <- data.frame(dir = basename(dirs), 
           count = unname(count_jpgs))

# sort
count_jpgs_df <- count_jpgs_df[with(count_jpgs_df, order(-count)),]
count_jpgs_df

# amongst the archaeological sites we have lots for
# LR9, ME2 & 3, LR12, mtbehn surface 2, japi
```



```{r}
# get_outlines code needs to start in workind director near image files
setwd(paste0(image_files, "/LR9-scans"))

# get_outlines code needs object which is called list_imgs
# we'll use the LR9 images first
list_imgs <- basename(jpgs[grep("LR9", jpgs)])

# now run the get_outlines code and watch the outlines appear...
code_folder <- "F:/My Documents/My Papers/conferences/SAA2014/Marwick and Malony/code/"

source(paste0(code_folder, "001_get_outlines.r"))

# now check to see if any outlines have <500 coords and exclude those
source(paste0(code_folder, "002_outlines_point_filter.r"))

# now scale and center the outlines (returns two plots, check to see all looks ok)
source(paste0(code_folder, "003_outlines_scale_center.r"))

# now check to see how many harmonics we need to represent the shapes
# probably best to run this line-by-line to iterate the number of harmonics
# it's going to make lots of plots and take a long time if you just source it.
paste0(code_folder, "004_outlines_inspect_harmonics.r")

# now compute eliptical fourier analysis
source(paste0(code_folder, "005_outlines_compute_EFA.r"))

# now compute PCA - this will make lots of plots, choose carefully!
# some customisation will be required for the coloured and transparent plots
source(paste0(code_folder, "006_outlines_compute_PCA_and_plot.r"))

# now compute MANOVA and tps - this will also make lots of plots
source(paste0(code_folder, "007_outlines_MANOVA_tps.r"))



